---
title: "Week 2"
output:
  html_document:
    df_print: paged
---

## Question 1
The weights listed below were recorded in the !Kung census, but heights
were not recorded for these individuals. Provide predicted heights and 89%
compatibility intervals for each of these individuals. That is, fill in the table
below, using model-based predictions.

```{r}
library(rethinking)
data("Howell1")
head(Howell1)
```


```{r}
sample_mu = rnorm(1e4, mean=178, sd=20)
sample_sigma = runif(1e4, min=0, max=50)
prior_h = rnorm(1e4, sample_mu, sample_sigma)
d = density(prior_h)
plot(d)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

